Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion Temperature \\ Gradient-Driven Turbulence

### 2023-06-22 presentation/presentation.tex
#39: Minor correction and animations for presentation

\title{Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion t
Temperature \\ Gradient-Driven Turbulence}
\subtitle{~}
\author{Manuel Lippert}
\institute{Theoretical Physics V}

@@

		Properties:
		\begin{enumerate}
			\item[(1)] <3-> They occur on a \textit{radial mesoscale} of order of $\rho_\mathrm{L} < 10\,\rhoth < R$
			\item[(2)] <4-> The structure are \textit{quasi stationary} in space and vary on time scales much longer than the typical turbulence time scales.
			\item[(3)] <5-> They have a \textit{typical amplitude} of the order of $10^{-1} \vth/R$.
			\item[(4)] <6-> Turbulent transport occurs in \textit{avalanches} with propagation strongly linked to the local $\exb$ shearing rate.
		\end{enumerate}
		\onslide<7->{
		\begin{center}
			\begin{tabular}{c c}
				$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$ & $\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)$ \\
			\end{tabular}
		\end{center}
		}
	\end{frame}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$ (normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$)) 
				\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <8-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<9->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\onslide<2-> $\wexb = \sum_{\kzf} \hatwexb(\kzf,t) \, \exp(\mathrm{i} \kzf \xcoord)$ \\[0.5cm]
			\onslide<3-> $\kzf = 2\pi \nzf/L_\xcoord$ \\[0.5cm]
			\onslide<4-> $\hatwexbamp = 2 |\hatwexb(\kzf,t)|$ \\[0.5cm]
			\begin{itemize}
				\item <5-> Zonal flow mode that dominates the $\exb$ staircase pattern are called \textbf{basic mode} 
				\item <6-> The basic mode exhibits the maximum amplitude in the spectrum $\hatwexbamp$
			\end{itemize}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{Restart Script}
		\pause

>>>>

\title{Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion
Temperature \\ Gradient-Driven Turbulence}
\subtitle{~}
\author{Manuel Lippert}
\institute{Theoretical Physics V}

@@

		\onslide<3-> Properties:
		\begin{enumerate}
			\item[(1)] <4-> They occur on a \textit{radial mesoscale} of order of $\rho_\mathrm{L} < 10\,\rhoth < R$
			\item[(2)] <5-> The structure are \textit{quasi stationary} in space and vary on time scales much longer than the typical turbulence time scales.
			\item[(3)] <6-> They have a \textit{typical amplitude} of the order of $10^{-1} \vth/R$.
			\item[(4)] <7-> Turbulent transport occurs in \textit{avalanches} with propagation strongly linked to the local $\exb$ shearing rate.
		\end{enumerate}
		\onslide<8->{
		\begin{center}
			\begin{tabular}{c c}
				$\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}$ & $\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)$ \\
			\end{tabular}
		\end{center}
		}
	\end{frame}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$ (normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$)) 
				\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <8-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\onslide<2-> $\wexb = \sum_{\kzf} \hatwexb(\kzf,t) \, \exp(\mathrm{i} \kzf \xcoord)$ \\[0.5cm]
			\onslide<2-> $\kzf = 2\pi \nzf/L_\xcoord$ \\[0.5cm]
			\onslide<2-> $\hatwexbamp = 2 |\hatwexb(\kzf,t)|$ \\[0.5cm]
			\begin{itemize}
				\item <3-> Zonal flow mode that dominates the $\exb$ staircase pattern are called \textbf{basic mode} 
				\item <4-> The basic mode exhibits the maximum amplitude in the spectrum $\hatwexbamp$
			\end{itemize}
		\end{center}
	\end{frame}
	\begin{frame}
		\frametitle{Restart Script}
		\pause
